### 2019-06-21 2-Chapters/2-Chapter/IEEE_WCNC_2018.git/IEEE_WCNC__2018__Paper__Lilian_Besson__07-17.tex
Proof reading Ch4

% ----------------------------------------------------------------------
\paragraph{Comparison with \ExpQ{}:}\label{sub:25:Exp4}
%
% - explain, but don't give pseudo-code ?
The \ExpQ{} algorithm dates from \cite{Auer02NonStochastic}, and for instance it is also well explained in Section~4.2 of \cite{Bubeck12}.
It is similar to \Aggr{}, presented in Algorithm~\ref{algo:25:Aggr},
but differs in the two following points.
%
The first difference is that $a\sim\pi^t$ is sampled first and the arm chosen by $\Alg_a$ is trusted, whereas \Aggr{}
needs to listen to the $N$ decisions to perform the updates on $\pi^{t}$.
Then, \ExpQ{} gives back an observation (\ie, a pair arm, reward) only to the last trusted algorithm
whereas \Aggr{} gives it to all algorithms.
%
The second difference is that after having computed the reward estimate $\widehat{r^a}(t)$, \ExpQ{} updates the estimated cumulative reward for each algorithm,
$\widetilde{R}_a(t) = \sum_{s=1}^{t} \widehat{r^a}(t) \times \indic(A^{s}_{a} = A^{s}_{\mathrm{aggr}})$.
%
Instead of updating $\pi^{t}$ multiplicatively as we do for our proposal, \ExpQ{} recomputes it, proportionally to
$\exp(\eta_t \widetilde{R}_a(t))$.
Note that there is no difference for the case of constant learning rates, and it does not differ much for decreasing learning rates as well.

We also note that \ExpQ{} uses \emph{losses} instead of rewards, with $\ell(t) = 1 - r(t)$, but this is only a change of vocabulary.

\paragraph{How to choose the learning rates $(\eta_t)$:}
%
The sequence of non-negative learning rates $(\eta_t)_{t \geq 1}$ used by \ExpQ{} can be arbitrary.
It can be constant but should be non-increasing \cite[Theorem 4.2]{Bubeck12}.
% helps to choose a good sequence.
If the horizon $T$ is known (and fixed), the best choice is given by $\eta_t \eqdef \eta = 2 \log(N) / (T K)$.
However, for real-world communication problems, it can be considered unrealistic to assume a fixed and known time horizon.
For more discussion on this hypothesis, we refer to Section~1 of our article \cite{Besson2018DoublingTricks}, that we shortly present in Appendix~\ref{app:2:DoublingTricks}.
%
Thus we prefer the alternative horizon-free choice of learning rates,
$\eta_t \eqdef \log(N) / (t K)$ suggested by \cite{Bubeck12}.
It is non-increasing, and is obtained by minimizing the upper-bound on the regret derived in \cite[pp48]{Bubeck12}.
%
We compared both approaches empirically, and the second one usually performs better.
We also stick to this sequence $(\eta_t)_{t \geq 1}$ of decreasing learning rates for \Aggr.

@@

% - explain the problem studied in the simulation
We focus on \emph{i.i.d.} MAB problems, with $K = 9$ arms\footnote{~Similar behaviors are observed for other values, \eg, trying up-to $K = 100$ gave the same results.}.
For Bernoulli problem, the first one uses $\boldsymbol{\mu}=[0.1,\dots,0.9]$, and is considered as a ``simple'' problem.
The second one is divided in three groups:
2 very bad arms ($\mu = 0.01, 0.02$), 5 average arms ($\mu = 0.3$ to $0.6$) and 3 very good arms ($\mu = 0.78, 0.8, 0.82$), and it is considered as a ``harder'' problem.
The horizon is set to $T = 20000$ (but its value is unknown to all algorithms), and simulations are repeated $1000$ times, to estimate the expected regret.
%
This empirical estimation of the expected regret $R_T$ is plotted below\footnote{~The Lai \& Robbins' logarithmic lower-bound \cite{LaiRobbins85} is also plotted. It corresponds to the second case in Theorem~\ref{thm:2:secondLogTLowerBound}. It is crucial to note that the lower-bound is only asymptotic, and as such one should not be surprised to see regret curves smaller than the lower-bound (\eg, for the easier Bernoulli problem in Figure~\ref{fig:25:EasyBernoulli}).},
as a function of $T$, comparing some algorithms $\Alg_1,\dots,\Alg_N$ (for $N=6$), and their aggregation with \Aggr{} (displayed in orange bold),
using the parameter-free learning rate sequence, $\eta_t \eqdef \log{N} / (t K)$.

Note that for each of the $N=1000$ simulations, we choose to generate all the rewards beforehand, \ie, one full matrix $(r_k(t))_{1\leq k \leq K, 1 \leq t \leq T}$ (for every repetition), in order to compare the algorithms on the same realizations%
\footnote{~Similar plots and similar results are obtained if this choice is not made, but it makes more sense to compare them against the same randomization. Note that this choice is the default in SMPyBandits, but the other possibility is implemented as well, by changing \texttt{cache\_rewards} to \texttt{true} or \texttt{false} in the \texttt{configuration} dictionary. See Section~\ref{sub:3:miniConfigurationFileSMPyBandits} for explanations on this \texttt{configuration.py} file, or the online documentation.}
of the MAB problem.

@@

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.07\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main_semilogy____env1-4_932221613383548446.pdf}
	\caption{On a ``simple'' Bernoulli problem (semilog-$y$ scale).}
	\label{fig:25:EasyBernoulli}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.07\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main____env2-4_932221613383548446.pdf}
	\caption{On a ``harder'' Bernoulli problem, they all have similar performances, except \LearnExp, and our proposal \Aggr{} outperforms its competitors.}
	\label{fig:25:HardBernoulli}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.07\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main____env3-4_932221613383548446.pdf}
	\caption{On an ``easy'' Gaussian problem, only \Aggr{} shows reasonable performances, thanks to BayesUCB and Thompson sampling.}
	\label{fig:25:EasyGaussian}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.07\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main_semilogy____env4-4_932221613383548446.pdf}
	\caption{On a harder problem, mixing Bernoulli, Gaussian, Exponential arms, with 3 arms of each type with the \emph{same mean}.}
	\label{fig:25:HarderMixed}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.07\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main_semilogx____env4-4_932221613383548446.pdf}
	\caption{The semilog-$x$ scale clearly shows the logarithmic growth of the regret for the best algorithms and our proposal \Aggr, even in a hard ``mixed'' problem (\emph{cf}. Figure~\ref{fig:25:HarderMixed}).}
	\label{fig:25:HarderMixed_semilogx}
\end{figure}

>>>>

% ----------------------------------------------------------------------
\paragraph{Comparison with \ExpQ}.\label{sub:25:Exp4}
%
% - explain, but don't give pseudo-code ?
The \ExpQ{} algorithm dates from \cite{Auer02NonStochastic}, and for instance it is also well explained in Section~4.2 of \cite{Bubeck12}.
It is similar to \Aggr{}, presented in Algorithm~\ref{algo:25:Aggr},
but differs in the two following points.
%
The first difference is that $a\sim\pi^t$ is sampled first and the arm chosen by $\Alg_a$ is trusted, whereas \Aggr{}
needs to listen to the $N$ decisions to perform the updates on $\pi^{t}$.
Then, \ExpQ{} gives back an observation (\ie, a pair arm, reward) only to the last trusted algorithm
whereas \Aggr{} gives it to all algorithms.
%
The second difference is that after having computed the reward estimate $\widehat{r^a}(t)$, \ExpQ{} updates the estimated cumulative reward for each algorithm,
$\widetilde{R}_a(t) = \sum_{s=1}^{t} \widehat{r^a}(t) \times \indic(A^{s}_{a} = A^{s}_{\mathrm{aggr}})$.
%
Instead of updating $\pi^{t}$ multiplicatively as we do for our proposal, \ExpQ{} recomputes it, proportionally to
$\exp(\eta_t \widetilde{R}_a(t))$.
Note that there is no difference for the case of constant learning rates, and it does not differ much for decreasing learning rates as well.

We also note that \ExpQ{} uses \emph{losses} instead of rewards, with $\ell(t) = 1 - r(t)$, but this is only a change of vocabulary.
A learner can equivalently play to maximize its cumulated rewards or to minimize its cumulated losses.
Most works on using expert advice and game theory usually prefer to think about losses, as for instance the book \cite{CesaLugosi06}.

\paragraph{How to choose $\eta_t$.}
%
The sequence of non-negative learning rates $(\eta_t)_{t \geq 1}$ used by \ExpQ{} can be arbitrary.
It can be constant but should be non-increasing \cite[Theorem 4.2]{Bubeck12}.
% helps to choose a good sequence.
If the horizon $T$ is known (and fixed), they advise to use $\eta_t \eqdef \eta = 2 \log(N) / (T K)$.
However, for real-world communication problems, it can be considered unrealistic to assume a fixed and known time horizon.
For more discussion on this hypothesis, we refer to Section~1 of our article \cite{Besson2018DoublingTricks}, that we shortly present in Appendix~\ref{app:2:DoublingTricks}.
%
Thus we prefer the alternative horizon-free choice of learning rates,
$\eta_t \eqdef \log(N) / (t K)$ suggested by \cite{Bubeck12}.
It is non-increasing, and is obtained by minimizing the upper-bound on the regret derived in \cite[pp48]{Bubeck12}.
%
We compared both approaches empirically, and the second one usually performs better.
We also stick to this sequence $(\eta_t)_{t \geq 1}$ of decreasing learning rates for \Aggr.

@@

% - explain the problem studied in the simulation
We focus on \emph{i.i.d.} MAB problems, with $K = 9$ arms.
Similar behaviors are observed for other values, \eg, trying up-to $K = 100$ gave the same results.
For Bernoulli problem, the first one uses $\boldsymbol{\mu}=[0.1,\dots,0.9]$, and is considered as a ``simple'' problem.
The second one is divided in three groups:
2 very bad arms ($\mu = 0.01, 0.02$), 5 average arms ($\mu = 0.3$ to $0.6$) and 3 very good arms ($\mu = 0.78, 0.8, 0.82$), and it is considered as a ``harder'' problem.
The horizon is set to $T = 20000$ (but its value is unknown to all algorithms), and simulations are repeated $1000$ times, to estimate the expected regret.
%
This empirical estimation of the expected regret $R_T$ is plotted below,
as a function of $T$, comparing some algorithms $\Alg_1,\dots,\Alg_N$ (for $N=6$), and their aggregation with \Aggr{} (displayed in orange bold),
using the parameter-free learning rate sequence, $\eta_t \eqdef \log{N} / (t K)$.

\textbf{Lower-bound.}
%
The Lai \& Robbins' logarithmic lower-bound \cite{LaiRobbins85} is also plotted. It corresponds to the second case in Theorem~\ref{thm:2:secondLogTLowerBound}. It is crucial to note that the lower-bound is only asymptotic, and as such one should not be surprised to see regret curves smaller than the lower-bound (\eg, for the easier Bernoulli problem in Figure~\ref{fig:25:EasyBernoulli})

\textbf{Comparing the algorithms against the same realizations.}
%
Note that for each of the $N=1000$ simulations, we choose to generate all the rewards beforehand, \ie, one full matrix $(r_k(t))_{k\in[K], t\in[T]}$, for each of the $N$ repetitions, in order to compare the algorithms on the same realizations of the MAB problem.
%
Similar plots and similar results are obtained if this choice is not made, but it makes more sense to compare them against the same randomization. Note that this choice is the default in SMPyBandits, but the other possibility is implemented as well, by changing \texttt{cache\_rewards} to \texttt{true} or \texttt{false} in the \texttt{configuration} dictionary. See Section~\ref{sub:3:miniConfigurationFileSMPyBandits} for explanations on this \texttt{configuration.py} file, or the online documentation.

@@

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main_semilogy____env1-4_932221613383548446.pdf}
	\caption{On a ``simple'' Bernoulli problem (semilog-$y$ scale).}
	\label{fig:25:EasyBernoulli}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main____env2-4_932221613383548446.pdf}
	\caption{On a ``harder'' Bernoulli problem, they all have similar performances, except \LearnExp, and our proposal \Aggr{} outperforms its competitors.}
	\label{fig:25:HardBernoulli}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main____env3-4_932221613383548446.pdf}
	\caption{On an ``easy'' Gaussian problem, only \Aggr{} shows reasonable performances, thanks to BayesUCB and Thompson sampling.}
	\label{fig:25:EasyGaussian}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main_semilogy____env4-4_932221613383548446.pdf}
	\caption{On a harder problem, mixing Bernoulli, Gaussian, Exponential arms, with 3 arms of each type with the \emph{same mean}.}
	\label{fig:25:HarderMixed}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main_semilogx____env4-4_932221613383548446.pdf}
	\caption{The semilog-$x$ scale clearly shows the logarithmic growth of the regret for the best algorithms and our proposal \Aggr, even in a hard ``mixed'' problem (\emph{cf}. Figure~\ref{fig:25:HarderMixed}).}
	\label{fig:25:HarderMixed_semilogx}
\end{figure}

### 2019-06-21 2-Chapters/2-Chapter/chapter25.tex
Proof reading Ch4

\paragraph{Naive approaches:}
%
On the one hand, a practitioner can decide to pick one algorithm, maybe because it seems efficient on other problems, or maybe because it is simple enough to be used in its application. It might be unrealistic to implement complicated algorithms on limited hardware such as embedded chips in a very low-cost IoT end-device, and for instance a practitioner could chose to only consider the $\UCB_1$ algorithm (or other low-cost algorithms).
%
On the other hand, if prior knowledge on the application at hand is available, one could implement some benchmarks, and compare a set of algorithms on different problems. If a leader appears clearly, it is then possible to choose it for the application.

\paragraph{Illustrative example:}
%
For instance, if you know that the considered problem can either have $K$ arms with very close means, or one optimal arm far away from the other, two versions of $\UCB_1$ will perform quite differently in the two problems:
using a large $\alpha$, \ie, favoring exploration, will give low regret in the first case,
while using a low $\alpha$, \ie, favoring exploitation, will give low regret in the second case.
One approach can be to use an intermediate value, as $\alpha=1/2$ suggested by theory, but another approach could be to consider an aggregated vote of different versions of $\UCB_1$, each running with a different value of $\alpha$ (\eg, in a logarithmic grid), and let another learning algorithm decide which value of $\alpha$ is the best \emph{for the problem at hand}.

>>>>

\paragraph{Naive approaches.}
%
On the one hand, a practitioner can decide to pick one algorithm, maybe because it seems efficient on other problems, or maybe because it is simple enough to be used in its application. It might be unrealistic to implement complicated algorithms on limited hardware such as embedded chips in a very low-cost IoT end-device, and for instance a practitioner could chose to only consider the $\UCB_1$ algorithm (or other low-cost algorithms).
%
On the other hand, if prior knowledge on the application at hand is available, one could implement some benchmarks, and compare a set of algorithms on different problems. If a leader appears clearly, it is then possible to choose it for the application.

\paragraph{Illustrative example.}
%
For instance, if you know that the considered problem can either have $K$ arms with very close means, or one optimal arm far away from the other, two versions of $\UCB_1$ will perform quite differently in the two problems:
using a large $\alpha$, \ie, favoring exploration, will give low regret in the first case and high regret in the second case,
while using a low $\alpha$, \ie, favoring exploitation, will obtain opposite performance.
A first approach can be to use an intermediate value, as $\alpha=1/2$ suggested by theory, but another approach could be to consider an aggregated vote of different versions of $\UCB_1$, each running with a different value of $\alpha$ (\eg, in a logarithmic grid), and let a ``master'' learning algorithm decide which value of $\alpha$ is the best \emph{for the problem at hand}.
